Loop

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

 this stupid figure has to get embedded    
 ![Fig1](./executableMS/Figures/Figure 1.png)

@@

![Fig2](./executableMS/Figures/Figure 2.png)

@@

## Results
Data characteristics and workflow
We used a dataset compiled by the International Mouse Phenotyping Consortium (Dickinson et al., 2016) (IMPC, dataset acquired 6/2018). To gain insight into systematic sex differences, we only included data of wildtype-strain adult mice, between 100 and 500 days of age. We removed cases with missing data, and selected measurements that were closest to 100 days of age (young adult) when multiple measurements of the same trait were available. To obtain robust estimates of sex dif- ferences, we only used data on traits that were measured in at least two different institutions (see workflow diagram, Figure 3).
Our dataset comprised 218 continuous traits (after initial data cleaning and pre-processing; Fig- ure 3). It contains information from 26,916 mice from nine wildtype strains that were studied across 11 institutions. We combined mouse strain/institution information to create a biological grouping variable (referred to as ‘population’ in Figure 3B; see also Supplementary file 1, Table 1 for details), and the mean and variance of a trait for each population was quantified. We assigned traits accord- ing to related procedures into functionally and/or procedurally related trait groups to enhance interpretability (referred to as ‘functional groups’ hereafter; see also Figure 3G). Our nine functional trait groups were: behaviour, morphology, metabolism, physiology, immunology, hematology, heart, hearing and eye (for the rationale of these functional groups and related details, see Methods and Supplementary file 1, Table 3).

>>>>

 this stupid figure has to get embedded    
 ![Fig1](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%201..png)

@@

 ![Fig2](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%202.png)

@@

## Results
Data characteristics and workflow
We used a dataset compiled by the International Mouse Phenotyping Consortium (Dickinson et al., 2016) (IMPC, dataset acquired 6/2018). To gain insight into systematic sex differences, we only included data of wildtype-strain adult mice, between 100 and 500 days of age. We removed cases with missing data, and selected measurements that were closest to 100 days of age (young adult) when multiple measurements of the same trait were available. To obtain robust estimates of sex dif- ferences, we only used data on traits that were measured in at least two different institutions (see workflow diagram, Figure 3).

 ![Fig3](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%203.png)

Our dataset comprised 218 continuous traits (after initial data cleaning and pre-processing; Figure 3). It contains information from 26,916 mice from nine wildtype strains that were studied across 11 institutions. We combined mouse strain/institution information to create a biological grouping variable (referred to as ‘population’ in Figure 3B; see also Supplementary file 1, Table 1 for details), and the mean and variance of a trait for each population was quantified. We assigned traits accord- ing to related procedures into functionally and/or procedurally related trait groups to enhance interpretability (referred to as ‘functional groups’ hereafter; see also Figure 3G). Our nine functional trait groups were: behaviour, morphology, metabolism, physiology, immunology, hematology, heart, hearing and eye (for the rationale of these functional groups and related details, see Methods and Supplementary file 1, Table 3).
